---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bikeHelpR

Helpful functions for interacting with data from <https://capitalbikeshare.com> and for use with the RStudio Bike Prediction example (<https://solutions.rstudio.com/example/bike_predict/>).

- Source code: <https://github.com/sol-eng/bikeHelpR>
- RStudio Package Manager: <https://packagemanager.rstudio.com/client/#/repos/1/packages/bikeHelpR>

## Installation

Install bikeHelpR from [RStudio Package Manager](https://packagemanager.rstudio.com/client/#/repos/1/packages/bikeHelpR).

```r
install.packages("bikeHelpR", repos = "https://packagemanager.rstudio.com/all/latest")
```

Install the latest development version of bikeHelpR from GitHub.

``` r
# install.packages("devtools")
devtools::install_github("sol-eng/bikeHelpR")
```

## Example

Check out the list of available data feeds:

```{r feeds}
library(bikeHelpR)

feeds <- feeds_urls()
print(feeds)
```

Get the latest data from the station_status feed:

```{r data}
url <- feeds |> 
  dplyr::filter(name == "station_status") |> 
  dplyr::pull(url)

station_status <- get_data(url)
dplyr::glimpse(station_status)
```

## Contributing

### Updating the docs

Regenerate the README using:

```r
devtools::load_all()
rmarkdown::render("README.Rmd", "all")
```
